---
title: "Individual Feedback Report Template"
date: today
title-block-banner: "#6baed6"
published-title: "Report generated"

format:
  html:
    theme: 
      light: default     
      dark: darkly    
    other-links:
      - text: BFI Information
        icon: info-circle
        href: https://www.rdocumentation.org/packages/psych/versions/2.5.6/topics/bfi
    include-after-body:
      text: |
        <footer class="footer">
          <hr> <!-- Optional horizontal line -->
          <p>Copyright 2026© Oui R. Awesome, Ltd.</p>
        </footer> 
    navbar:
toc: true
lightbox: true

execute: 
  echo: false
  warning: false
  error: false
---

```{r exampledata}

library(psych)
data(bfi)            ## fresh load each time (no mistake RE-recodes)

bfi$A1 <- 7-bfi$A1   ## Item recodes

bfi$C4 <- 7-bfi$C4
bfi$C5 <- 7-bfi$C5

bfi$E1 <- 7-bfi$E1
bfi$E2 <- 7-bfi$E2

bfi$O2 <- 7-bfi$O2
bfi$O5 <- 7-bfi$O5


respondent <- bfi[2800,]    ## isolating 1 respondent
norms      <- bfi[-2800,]

respondent[29] <- "Nörm N Nörmman"
colnames(respondent)[29] <- "name"

```

```{r norms}

agree_norm <- rowMeans(norms[1:5], na.rm=TRUE) 
cons_norm  <- rowMeans(norms[6:10], na.rm=TRUE)
extra_norm <- rowMeans(norms[11:15], na.rm=TRUE)
neuro_norm <- rowMeans(norms[16:20], na.rm=TRUE)
open_norm  <- rowMeans(norms[21:25], na.rm=TRUE)

agree_mean <- mean(agree_norm, na.rm = TRUE)
agree_sd   <- sd(agree_norm, na.rm = TRUE)

cons_mean  <- mean(cons_norm, na.rm = TRUE)
cons_sd    <- sd(cons_norm, na.rm = TRUE)

extra_mean <- mean(extra_norm, na.rm = TRUE)
extra_sd   <- sd(extra_norm, na.rm = TRUE)

neuro_mean <- mean(neuro_norm, na.rm = TRUE)
neuro_sd   <- sd(neuro_norm, na.rm = TRUE)

open_mean  <- mean(open_norm, na.rm = TRUE)
open_sd    <- sd(open_norm, na.rm = TRUE)

```

```{r scoring}

agree <- rowMeans(respondent[1:5], na.rm=TRUE) 
cons  <- rowMeans(respondent[6:10], na.rm=TRUE)
extra <- rowMeans(respondent[11:15], na.rm=TRUE)
neuro <- rowMeans(respondent[16:20], na.rm=TRUE)
open  <- rowMeans(respondent[21:25], na.rm=TRUE)

## Scale scores (μ=100, σ=15)

agree_ss <- round(((((agree-agree_mean)/agree_sd)*15)+100),0)
cons_ss  <- round(((((cons-cons_mean)/cons_sd)*15)+100),0)
extra_ss <- round(((((extra-extra_mean)/extra_sd)*15)+100),0)
neuro_ss <- round(((((neuro-neuro_mean)/neuro_sd)*15)+100),0)
open_ss  <- round(((((open-open_mean)/open_sd)*15)+100),0)

scores <- rbind(agree_ss, cons_ss, extra_ss, neuro_ss, open_ss)
dimension <- c("Agreeableness", 
               "Conscientiousness", 
               "Extraversion",
               "Neuroticism",
               "Openness")
toplot <- as.data.frame(cbind(dimension, scores))
colnames(toplot)[2] <- "Standard Score"

toplot$`Standard Score` <- as.numeric(as.character(toplot$`Standard Score`))

```

## Assessment information

The BFI consists of 25 personality items and 3 demographics (gender, education, and age). Responses to the 25 personality items determine an individuals standing along 5 personality dimensions:

+ **Extraversion** -- an orientation of interest and energies ranging from the outer world of people and things to the inner world of subjective experience 
+ **Conscientiousness** -- a tendency to be organized, responsible, and hardworking/industrious 
+ **Agreeableness** -- tendency to act in a cooperative, unselfish manner 
+ Openness to experience (**Openness**) -- tendency to be open to new aesthetic, cultural, or intellectual experiences
+ **Neuroticism** -- chronic levels of emotional instability and proneness to psychological distress

## Results summary for `r respondent$name`:

There were `r sum(is.na(respondent[1:25]))` missing responses across 25 personality item administrations.

When compared against responses of `r nrow(norms)` other individuals, `r respondent$name`'s personality profile can be extracted from @fig-radarplot and @fig-barplot.

```{r}
#| label: fig-radarplot
#| fig-cap: "Standard score radar plot across 5 dimensions"
#| 
library(plotly)

fig <- plot_ly(
    type = 'scatterpolar',
    r = toplot$`Standard Score`,
    theta = toplot$dimension,
    fill = 'toself'
  ) 
fig <- fig %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(50,120)
      )
    ),
    showlegend = F
  )

fig

```

```{r}
#| label: fig-barplot
#| fig-cap: "Standard score dotplot across 5 dimensions"

library(ggplot2)
ggplot(toplot, aes(x = reorder(dimension, `Standard Score`), y=`Standard Score`)) +
  geom_segment( aes(y=0, yend=`Standard Score`)) +
  geom_point(size=9.5, color="#0000d1", alpha=.8) +      ## adding border
  geom_point(size=8, color="#6baed6", alpha=.8) + 
  geom_text(aes(label = `Standard Score`), color = "black", size = 3.5) +
  labs(x="",y="") +
  scale_y_continuous(breaks=c(80, 100, 120), labels = c("low", "average", "high")) +
  theme(legend.position="none", text=element_text(family="Times")) +
  coord_flip(ylim=c(50,120))
```

## Interpretation and Summary

Scores above 100 indicate greater than average whereas scores below 100 indicate less than average. 

# Appendix

Reported scores have an average of 100 and standard deviation of 15.



